---
title: "cpam: Shape-constrained changepoint additive models for time series omics data"
output: 
  github_document:
    toc: true
    toc_depth: 2
    html_preview: false
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = ".")
  })
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


## Analysis of time series omics data with cpam 

**cpam** (**c**hange**p**oint **a**dditive **m**odels) fits smooth shape-constrained additive models to omics count data.

## Overview
Brief description (2-3 sentences) of what cpam does and its key features.

## Installation
```{r, eval = FALSE}
# Installation code here
remotes::install_github("l-a-yates/cpam")
```

## Usage
Load package and create a tibble for the experimental design.
```{r, echo = TRUE}
library(cpam)

exp_design
```
You will need a tibble with transcript-to-gene mapping. E.g.,
```{r}
t2g
```

